A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-26 sections/Metatheory.tex
S3 last paragraph, pointing to S4.2
further revision of 4.1

\hfill \framebox{$\Om \rto \Om'$} \hfill $\Om$ reduces to $\Om'$.
\begin{gather*}
\begin{aligned}
\Om,a &\rto \Om \qquad \Om,x:A \rto \Om\\
\Om\Vdash A\le B &\rto \Om \text{ when } \|\Om\| \vdash A\le B\\
\Om\Vdash e\Lto A &\rto \Om \text{ when } \|\Om\| \vdash e\Lto A\\
\Om\Vdash e\To_a \jg &\rto \Om\Vdash[A/a]\jg \text{ when } \|\Om\| \vdash e\To A\\
\Om\Vdash \appInfAlg{A}{e} &\rto \Om\Vdash[C/a]\jg \text{ when } \|\Om\| \vdash \appInf{A}{e}{C}\\
\end{aligned}
\end{gather*}
\caption{Declarative Worklist Typing.\bruno{I think your names for the
  two relations/definitions aren't great. I think what you're defining
here should be called transfer. The previous relation should probably
be called something different. Maybe something like Declarative
worklist instantiation/realization for the previous relation?}}
\label{fig:decl:worklist}
\end{figure}

Figure~\ref{fig:decl:worklist} defines a declarative version $\Om \sto \Om'$ of
the algorithmic reduction rules, which relates the declarative worklists to the
declarative type system, by checking every judgement entry in the worklist with
the help of the corresponding conventional declarative judgement. Recall that
the worklist consists of an interleaving of the typing context with judgments.
By means of the auxiliary function $\|\Om\|$ we can extracts the typing context
out of it, for use in the conventional declarative judgments. What is does to
obtain the typing context is simply erase the judgment entries from the
worklist.

>>>>

\hfill \framebox{$\Om \rto \Om'$} \hfill Declarative transfer.
\begin{gather*}
\begin{aligned}
\Om,a &\rto \Om \\  \Om,x:A & \rto \Om\\
\Om\Vdash A\le B &\rto \Om &\text{ when } \|\Om\| \vdash A\le B\\
\Om\Vdash e\Lto A &\rto \Om & \text{ when } \|\Om\| \vdash e\Lto A\\
\Om\Vdash e\To_a \jg &\rto \Om\Vdash[A/a]\jg & \text{ when } \|\Om\| \vdash e\To A\\
\Om\Vdash \appInfAlg{A}{e} &\rto \Om\Vdash[C/a]\jg & \text{ when } \|\Om\| \vdash \appInf{A}{e}{C}\\
\end{aligned}
\end{gather*}
\caption{Declarative Transfer.}
\label{fig:decl:worklist}
\end{figure}

Figure~\ref{fig:decl:worklist} defines a declarative version $\Om \sto \Om'$ of
the algorithmic reduction rules, which transfers judgements in the declarative worklists to the
declarative type system, by checking every judgement entry in the worklist with
the help of the corresponding conventional declarative judgement. Recall that
the worklist consists of an interleaving of the typing context with judgments.
By means of the auxiliary function $\|\Om\|$ we can extracts the typing context
out of it, for use in the conventional declarative judgments. What is does to
obtain the typing context is simply erase the judgment entries from the
worklist.
